Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-22 cav2017/cav2017.tex
response to one of A's comments

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined
In this section we outline the general architecture of the program synthesiser used in both approaches\todo{which approaches?}. 
We then detail the two methods of solution generalisation that we compare.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined
In this section we outline the general architecture of the program synthesiser used in both approaches%\todo{which approaches?}. 
We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.
